### 2014-02-24 paper/retrofit.tex
.
Straight arrow-ify things that are implicitly applying step.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\begin{figure}
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
  &|erase il (tconf id il' ie) =| \begin{cases}
    %|lconf bullet bullet bullet bullet| & |il' cantFlowTo il| \\
    |bullet| & |il' cantFlowTo il| \\
    |fullconf id il' (erase il tS) (erase il ie)| & \text{otherwise}
  \end{cases} \\
  %&|erase il iS [i mapsto Q] = iS [i mapsto (erase il Q)]|\\
  &|erase il Q = filter il Q|\\
  &|erase il (send ie1 ie2 ie3) =| \begin{cases}
    |send ie1 ie2 bullet| & |ie2 cantFlowTo il| \\
    |send ie1 ie2 (erase il ie3)| & \text{otherwise}
  \end{cases} \\
  &\text{In all other cases, |erasef il| is applied homomorphically.}
\end{align*}
\caption{Erasure function.}
\end{figure}

@@

\and
\inferrule[I-getLabel]
{ }
{|
niconf iS id il getLabel
.->
niconf iS id il il
|}

\and
\inferrule[I-setLabel]
{ |il canFlowTo il'| }
{|
niconf iS id il (setLabel il')
.->
niconf iS id il' unit
|}
%{|fresh (id')|}

\and
\inferrule[I-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ id' mapsto (il', id,  ie) , Q ]|
}
{|
niconf iS  id il (send id' il' ie)
.->
niconf iS' id il unit
|}

\and
\inferrule[I-recv]
{
| filter il (iS(id)) = io1 , ... , iok , (il', id', ie')|\\
| iS' = iS[id mapsto io1 , ... , iok]|\\
}
{|
niconf iS  id il (ix1, ix2 <= recv. ie1 ie2)
.->
niconf iS' id il ({ie'/ix1,id'/ix2} ie1)
|}

\and
\inferrule[I-noRecv]
{
| filter il (iS(id)) = nil|\\
| iS' = iS[id mapsto nil]|
}
{|
niconf iS  id il (ix1, ix2 <= recv. ie1 ie2)
.->
niconf iS' id il ie2
|}

@@

\and
\inferrule[I-border]
{ }
{|
niconf iS id il (IT (TI (ie)))
.->
niconf iS id il ie
|}

@@

>>>>

\begin{figure}
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
  &|erase il (tconf id il' ie) =| \begin{cases}
    %|lconf bullet bullet bullet bullet| & |il' cantFlowTo il| \\
    |bullet| & |il' cantFlowTo il| \\
    |fullconf id il' (erase il tS) (erase il ie)| & \text{otherwise}
  \end{cases} \\
  %&|erase il iS [i mapsto Q] = iS [i mapsto (erase il Q)]|\\
  &|erase il Q = filter il Q|\\
  &|erase il (send id il' ie) =| \begin{cases}
    |send ie1 ie2 bullet| & |il' cantFlowTo il| \\
    |send id il' (erase il ie)| & \text{otherwise}
  \end{cases} \\
  &\text{In all other cases, |erasef il| is applied homomorphically.}
\end{align*}
\caption{Erasure function.}
\end{figure}

@@

\and
\inferrule[I-getLabel]
{ }
{|
niconf iS id il getLabel
->
niconf iS id il il
|}

\and
\inferrule[I-setLabel]
{ |il canFlowTo il'| }
{|
niconf iS id il (setLabel il')
->
niconf iS id il' unit
|}
%{|fresh (id')|}

\and
\inferrule[I-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ id' mapsto (il', id,  ie) , Q ]|
}
{|
niconf iS  id il (send id' il' ie)
->
niconf iS' id il unit
|}

\and
\inferrule[I-recv]
{
| filter il (iS(id)) = io1 , ... , iok , (il', id', ie')|\\
| iS' = iS[id mapsto io1 , ... , iok]|\\
}
{|
niconf iS  id il (ix1, ix2 <= recv. ie1 ie2)
->
niconf iS' id il ({ie'/ix1,id'/ix2} ie1)
|}

\and
\inferrule[I-noRecv]
{
| filter il (iS(id)) = nil|\\
| iS' = iS[id mapsto nil]|
}
{|
niconf iS  id il (ix1, ix2 <= recv. ie1 ie2)
->
niconf iS' id il ie2
|}

@@

\and
\inferrule[I-border]
{ }
{|
niconf iS id il (IT (TI (ie)))
->
niconf iS id il ie
|}

@@

\begin{proof}[Proof of Lemma~\ref{lemma:tsni}]
  We proof the lemma by induction on the derivation
  for~\eqref{eq:tsni-lemma-lhs}, and consider all possible rules that
  could have been used to make the reduction step.
  \begin{description}
    \item[Case \textsc{I-done}] 
    \item[Case \textsc{I-noStep}] 
    \item[Case \textsc{I-fork}] 
    \item[Case \textsc{I-setLabel}]
  \end{description}
\end{proof}
